Trends and Challenges in Toronto’s Homeless Population (2018-2024)

### 2024-09-26 paper/paper.qmd
change the subtitle

---
title: "Trends and Challenges in Toronto’s Homeless Population (2018-2024)"
subtitle: "A Focus on Demographics and Chronic Homelessness"
author: 
  - Jianing Li
thanks: "Code and data are available at: https://github.com/JianingLi1225/Toronto_Homeless"
date: today
date-format: long
abstract: "Toronto’s homeless population experienced changes between 2018 and 2024, with key trends in age, gender, and chronic homelessness. Using data from the Toronto Shelter System, this paper examines these trends and the effects of the COVID-19 pandemic. The results show that males aged 35-44 are the largest demographic, and the number of chronically homeless individuals has increased. Understanding these dynamics is essential for developing more effective policies to address homelessness and improve long-term housing stability."
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---

>>>>

---
title: "Trends and Challenges in Toronto’s Homeless Population (2018-2024)"
subtitle: "Middle-Aged Males Leading the Homeless Population with Continued Growth in Chronic Homelessness"
author: 
  - Jianing Li
thanks: "Code and data are available at: https://github.com/JianingLi1225/Toronto_Homeless"
date: today
date-format: long
abstract: "Toronto’s homeless population experienced changes between 2018 and 2024, with key trends in age, gender, and chronic homelessness. Using data from the Toronto Shelter System, this paper examines these trends and the effects of the COVID-19 pandemic. The results show that males aged 35-44 are the largest demographic, and the number of chronically homeless individuals has increased. Understanding these dynamics is essential for developing more effective policies to address homelessness and improve long-term housing stability."
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---
